---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)

```

I'm going to start by just getting all the graphs together in one space. 

**Remember, before adding the map stuff, make sure to do an add, commit and push and maybe find a way to stop the html file being too huge**

**Slide 1**

No visual content

**Slide 2**

No visual content, although may need a screen shot of the type of dataframe. Also, could do some screenshots of
some of the planning documents that were used could be useful 

**Slide 3**

[Graph 1]

```{r}
graph_1_data <- read_csv("data/presentation_data/graph_1_all_means_scot_groups_less_11.csv") %>% clean_names()
```

```{r}
graph_1_data
```


```{r}
graph_1_data <-
graph_1_data %>% 
  arrange(desc(type), desc(mean)) %>% 
  mutate(class = factor(class, levels = class)) %>% 
  mutate(class = recode(class, "Adults (non pension, no children)" = "Adults (-psn, -child)"))
```


```{r}
# Need to work out how to separate types 

graph_1_data %>%
  ggplot() + 
  aes(x = class, y = mean, fill = type) +
  geom_col(colour = "black", size = 0.2) +
  theme_minimal() +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 10)) +
  coord_flip() +
  scale_fill_brewer(palette = "Set3") +
  labs(title = "Percentage of Population Within a 10-minute Walk of Green Space",
          subtitle = "Mean figures between 2013 - 2019 - Scotland") +
  xlab("") +
  ylab("%") +
  labs(fill = "Category") +
  theme(plot.title = element_text(size = 12.0),
        plot.subtitle = element_text(size = 10.0),
        legend.key.size = unit(0.4, "cm"),
        legend.key.width = unit(0.4, "cm"))
  
  
```













**Slide 7**

[Graph 7] - maybe just try and use the other datasets or, worse comes to worse, the original gb_data_set 