---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(ggplot2)
library(GGally)
library(here)

neighbourhood_comp_data <- read_csv("data/complete_neighbourhood_rating.csv") %>% clean_names()
community_comp_data <- read_csv("data/complete_community_belonging.csv") %>% clean_names()
local_authority_codes <- read_csv("data/Local_Authority_Districts_Codes.csv") %>% clean_names()
green_blue_comp_data <- read_csv("data/complete_dist_blue_green.csv") %>% clean_names()


```

```{r}
scot_local_auth_codes <-
local_authority_codes %>% 
  filter(str_detect(lad19cd, "S12")) %>% 
  select(lad19cd, lad19nm) %>% 
  rename(feature_code = lad19cd,
         local_authority = lad19nm)
```

```{r}
neigh_with_las_data <-
full_join(neighbourhood_comp_data, scot_local_auth_codes, "feature_code")

neigh_with_las_data <-
neigh_with_las_data %>% 
  mutate(local_authority = if_else(feature_code == "S92000003", "Scotland", local_authority))

neigh_with_las_data
```

```{r}
commun_with_las_data <-
full_join(community_comp_data, scot_local_auth_codes, "feature_code")

commun_with_las_data <-
commun_with_las_data %>% 
  mutate(local_authority = if_else(feature_code == "S92000003", "Scotland", local_authority))

commun_with_las_data
```

```{r}
commun_filtered <-
commun_with_las_data %>%
  filter(measurement == "Percent") %>% 
  select(-c(feature_code, units, measurement))

neigh_filtered <-
neigh_with_las_data %>%
  filter(measurement == "Percent") %>% 
  select(-c(feature_code, units, measurement))
```

```{r}
neigh_filtered

commun_filtered
```
```{r}
neigh_pivot_wide <-
neigh_filtered %>% 
pivot_wider(names_prefix = "nr_", names_from = neighbourhood_rating, values_from = value)

commun_pivot_wide <-
commun_filtered %>% 
pivot_wider(names_prefix = "com_bel_", names_from = community_belonging, values_from = value)
```

```{r}
#This may be slightly dodgy since we're not completely sure that the two data sets refer to the same individuals. We're probably going to end up with quite a lot of missing values as well

neigh_comm_original_join <-
full_join(neigh_pivot_wide, commun_pivot_wide) %>% 
  clean_names()
```

```{r}
just_walking_distance_neigh_comm <-
neigh_comm_original_join %>% 
  filter(walking_distance_to_nearest_greenspace != "All")

just_walking_distance_neigh_comm
```

```{r}
neigh_comm_original_join %>%
  ggplot() +
  aes(x = nr_very_good, y = com_bel_very_strongly, color = walking_distance_to_nearest_greenspace) +
  geom_point()
```

```{r}
just_walking_distance_neigh_comm %>% 
  ggplot() +
  aes(x = nr_very_good, y = com_bel_very_strongly, color = walking_distance_to_nearest_greenspace) +
  geom_point()
```

```{r}
just_walking_distance_neigh_comm %>% 
  ggplot() +
  aes(x = nr_fairly_good, y = com_bel_fairly_strongly, color = walking_distance_to_nearest_greenspace) +
  geom_point()
```

```{r}
just_walking_distance_neigh_comm %>% 
  ggplot() +
  aes(x = nr_fairly_poor, y = com_bel_not_very_strongly, color = walking_distance_to_nearest_greenspace) +
  geom_point()
```

```{r}
just_walking_distance_neigh_comm %>% 
  ggplot() +
  aes(x = nr_very_poor, y = com_bel_not_at_all_strongly, color = walking_distance_to_nearest_greenspace) +
  geom_point()
```

Cool, so we've plotted some of the relationships between the the neighbourhood ratings and the community belonging ratings, based on the fact that they both pretty much exist on a evenly spaced four-point scale (with an extra don't know section each). 

Now let's see if we can add the green/blue space data and even if we can use all of this to start forming a model. 

```{r}
gb_full_clean <-
full_join(green_blue_comp_data, scot_local_auth_codes, "feature_code") %>% 
  mutate(local_authority = if_else(feature_code == "S92000003", 
                                   "Scotland", 
                                   local_authority)) %>% 
  filter(measurement == "Percent") %>% 
  select(-c(feature_code, units, measurement)) %>% 
    pivot_wider(names_from = distance_to_nearest_green_or_blue_space,
              values_from = value) %>% 
  clean_names() %>% 
  mutate(less_than_11_mins = a_5_minute_walk_or_less + within_a_6_10_minute_walk)

gb_full_clean
```

```{r}
# There must be something going on with the extra walking_distance_column which might effect any join. I'm guessing it would just mean gaps though. 
#setdiff(gb_full_clean$date_code:local_authority, neigh_comm_original_join$date_code:)
```

```{r}
#Pretty sure this won't work. The figures for percentage of people in certain walking distance just wouldn't relate to the neighbourhood and community figures the way we'd want them to.
full_join(gb_full_clean, neigh_comm_original_join) %>% 
  filter(walking_distance_to_nearest_greenspace == "All")
```

Need to have a good think what is actually being joined here and in what manner it may be inaccurate.

Let's just go with making a single model based on the combined neighbourhood and community dataframes. I'm going to first try this with the entire dataset and then try it with the dataset that has no "All's" in the walking_distance category. 

```{r}
summary(neigh_comm_original_join)
```

```{r}
neigh_comm_original_join %>% 
summarise(across(.fns = ~sum(is.na(.x))))
```

The NAs are in the ratings columns representing percentage of people who have this opinion. My gut says that we should think about making these have values of either 0 or 1. We could always try both and see what happens I suppose...

**A note on where we are as we start thinking about variable engineering**

Overall, no matter how we wrangle our data, our dependent variables will be our household rating and community rating variables.

In our current dataset, these are split into 5 different categories for each (including "don't know"). These scores are given as percentages and we will therefore be treating them like continuous variables. 

These variables are currently in a wide format. This means that theoretically if we wanted to predict what a particular score for "very good" would look like for a particular group, we would need to make this the single dependent variable in any model.

```{r}

```

